\newpage

\begin{usecase}
  \addheading{Use-Case Description}
  \addsingletwocolumnrow{Name}{oeAddUser}
  \addsingletwocolumnrow{Scope}{System}
  \addsingletwocolumnrow{Altitude}{subfunction}
   
  \addrowheading{Parameters}
  \addnumberedsinglerow{}{\msrcode{UserID:dtUserID} - the
  user's identification.}
  \addnumberedsinglerow{}{\msrcode{Login:dtLogin} - the username of the
  user.}
  \addnumberedsinglerow{}{\msrcode{Password:dtPassword} - the password of the
  user.}
   \addnumberedsinglerow{}{\msrcode{TokenID:dtTokenID} - the a unique
   identifier for the users token.}
   \addnumberedsinglerow{}{\msrcode{Usertyep:etUserType} - the Type of user [Coordinator, DomainExpert or EMS]}
  \addnumberedsinglerow{}{\msrcode{CoordinatorDomain:ctDomain} – the domains of expertise of a coordinator.}
  
  \addrowheading{Primary actor(s)}
  \addnumberedsinglerow{}{\msrcode{actAdministrator[active]}}
  
  \addrowheading{Secondary actor(s)}
  \addnumberedsinglerow{}{\msrcode{actCoordinator[passive]}}
  \addnumberedsinglerow{}{\msrcode{actDomainExpert[passive]}}
  \addnumberedsinglerow{}{\msrcode{actEMS[passive]}}
  
  \addrowheading{Goal(s) description}
  \addsinglerow{the \msrcode{actAdministrator}'s goal is to delete
  new user to the system so he/she can safely use the
  system.}
  
  \addrowheading{Reuse}
  \addnumberedsinglerow{}{none}

  \addrowheading{Protocol condition(s)}
  \addnumberedsinglerow{}{the \msricrash system has been deployed.}
  
  \addrowheading{Pre-condition(s)}
  \addnumberedsinglerow{}{none}
  
  \addrowheading{Main post-condition(s)}
  \addnumberedsinglerow{}{A new user has been added to
  the system.}
  \addnumberedsinglerow{}{The new user can use the
  system safely.}
  
  \addrowheading{Main success steps}
  \addalphanumberedsinglerow{}{the actor \msrcode{actAdmnistrator} sends the
  message
  \msrucname{oeAddUser(CoordinatorID,Login,Password,TokenID,CoordinatorDomain)} to the system.}
  
  \addrowheading{Step Constraints Ordering and Extensions}
  \addnumberedsinglerow{}{none}
  
  \addrowheading{Additional Information}
  \addsinglerow{When creating Coordinator you must specify his domains of expertise. Only users of the type Coordinator need to have specific Domains.}
  
\end{usecase} 